Evaluating Variable Importances

### 2019-07-12 Scripts/evaluating_variable_importances.Rmd
added 5kb results

@@

@@

```{r}
#GM12878
all_varimps_gm12878_tfbs <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878_tfbs) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[order(rowMeans(all_varimps_gm12878_tfbs[,-1]), decreasing = TRUE),]
all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[1:20,]
all_varimps_gm12878_tfbs <- melt(all_varimps_gm12878_tfbs)

a <- ggplot(all_varimps_gm12878_tfbs, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("Transcription Factor") +
  ggtitle("GM12878") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

#K562
all_varimps_K562_tfbs <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562_tfbs) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562_tfbs <- all_varimps_K562_tfbs[order(rowMeans(all_varimps_K562_tfbs[,-1]), decreasing = TRUE),]
all_varimps_K562_tfbs <- all_varimps_K562_tfbs[1:20,]
all_varimps_K562_tfbs <- melt(all_varimps_K562_tfbs)

b <- ggplot(all_varimps_K562_tfbs, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  ggtitle("K562") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "lightblue",
                      midpoint = 50,
                      high = muted("blue"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

@@

@@

@@

```{r}
#GM12878
all_varimps_gm12878_chromstates <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878_chromstates) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878_chromstates <- all_varimps_gm12878_chromstates[order(rowMeans(all_varimps_gm12878_chromstates[,-1]), decreasing = TRUE),]
#all_varimps_gm12878_chromstates <- all_varimps_gm12878_chromstates[1:20,]
all_varimps_gm12878_chromstates <- melt(all_varimps_gm12878_chromstates)

a <- ggplot(all_varimps_gm12878_chromstates, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("Chromatin State") +
  ggtitle("GM12878") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

#K562
all_varimps_K562_chromstates <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562_chromstates) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562_chromstates <- all_varimps_K562_chromstates[order(rowMeans(all_varimps_K562_chromstates[,-1]), decreasing = TRUE),]
#all_varimps_K562_chromstates <- all_varimps_K562_chromstates[1:20,]
all_varimps_K562_chromstates <- melt(all_varimps_K562_chromstates)

b <- ggplot(all_varimps_K562_chromstates, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  ggtitle("K562") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "lightblue",
                      midpoint = 50,
                      high = muted("blue"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

@@

@@

@@

```{r}
#GM12878
all_varimps_gm12878_histones <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878_histones) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878_histones <- all_varimps_gm12878_histones[order(rowMeans(all_varimps_gm12878_histones[,-1]), decreasing = TRUE),]
#all_varimps_gm12878_histones <- all_varimps_gm12878_histones[1:20,]
all_varimps_gm12878_histones <- melt(all_varimps_gm12878_histones)

a2 <- ggplot(all_varimps_gm12878_histones, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("Histone Modification") +
  ggtitle("GM12878") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

#K562
all_varimps_K562_histones <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562_histones) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562_histones <- all_varimps_K562_histones[order(rowMeans(all_varimps_K562_histones[,-1]), decreasing = TRUE),]
#all_varimps_K562_histones <- all_varimps_K562_histones[1:20,]
all_varimps_K562_histones <- melt(all_varimps_K562_histones)

b2 <- ggplot(all_varimps_K562_histones, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  ggtitle("K562") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "lightblue",
                      midpoint = 50,
                      high = muted("blue"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

>>>>

###5kb

```{r}
varimp_gm12878_5kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_gm12878_5kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_gm12878_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_gm12878_5kb <- data.frame(Feature = rownames(varimp_gm12878_5kb),
                                  aveimp5kb = rowMeans(varimp_gm12878_5kb, na.rm = TRUE),
                                  sdimp5kb = apply(varimp_gm12878_5kb,1, sd, na.rm = TRUE))
rownames(varimp_gm12878_5kb) <- NULL
```

@@

###5kb

```{r}
varimp_K562_5kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_K562_5kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

		varimp_K562_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_K562_5kb <- data.frame(Feature = rownames(varimp_K562_5kb),
                                  aveimp5kb = rowMeans(varimp_K562_5kb, na.rm = TRUE),
                                  sdimp5kb = apply(varimp_K562_5kb,1, sd, na.rm = TRUE))
rownames(varimp_K562_5kb) <- NULL
```

@@

```{r}
#GM12878
all_varimps_gm12878_tfbs <- cbind.data.frame(varimp_gm12878_5kb$Feature,
                                        varimp_gm12878_5kb$aveimp5kb,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878_tfbs) <- c("Feature", "ave10kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[order(rowMeans(all_varimps_gm12878_tfbs[,-1]), decreasing = TRUE),]
all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[1:20,]
all_varimps_gm12878_tfbs <- melt(all_varimps_gm12878_tfbs)

a <- ggplot(all_varimps_gm12878_tfbs, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("Transcription Factor") +
  ggtitle("GM12878") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

#K562
all_varimps_K562_tfbs <- cbind.data.frame(varimp_K562_5kb$Feature,
                                        varimp_K562_5kb$aveimp5kb,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562_tfbs) <- c("Feature", "ave5kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562_tfbs <- all_varimps_K562_tfbs[order(rowMeans(all_varimps_K562_tfbs[,-1]), decreasing = TRUE),]
all_varimps_K562_tfbs <- all_varimps_K562_tfbs[1:20,]
all_varimps_K562_tfbs <- melt(all_varimps_K562_tfbs)

b <- ggplot(all_varimps_K562_tfbs, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  ggtitle("K562") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "lightblue",
                      midpoint = 50,
                      high = muted("blue"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

@@

###5kb

```{r}
varimp_gm12878_5kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_gm12878_5kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

		varimp_gm12878_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_gm12878_5kb <- data.frame(Feature = rownames(varimp_gm12878_5kb),
                                  aveimp5kb = rowMeans(varimp_gm12878_5kb, na.rm = TRUE),
                                  sdimp5kb = apply(varimp_gm12878_5kb,1, sd, na.rm = TRUE))
rownames(varimp_gm12878_5kb) <- NULL

@@

###5kb

```{r}
varimp_K562_5kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_K562_5kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_K562_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_K562_5kb <- data.frame(Feature = rownames(varimp_K562_5kb),
                                  aveimp5kb = rowMeans(varimp_K562_5kb, na.rm = TRUE),
                                  sdimp5kb = apply(varimp_K562_5kb,1, sd, na.rm = TRUE))
rownames(varimp_K562_5kb) <- NULL

@@

```{r}
#GM12878
all_varimps_gm12878_chromstates <- cbind.data.frame(varimp_gm12878_5kb$Feature,
                                        varimp_gm12878_5kb$aveimp5kb,            
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878_chromstates) <- c("Feature", "ave5kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878_chromstates <- all_varimps_gm12878_chromstates[order(rowMeans(all_varimps_gm12878_chromstates[,-1]), decreasing = TRUE),]
#all_varimps_gm12878_chromstates <- all_varimps_gm12878_chromstates[1:20,]
all_varimps_gm12878_chromstates <- melt(all_varimps_gm12878_chromstates)

a <- ggplot(all_varimps_gm12878_chromstates, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("Chromatin State") +
  ggtitle("GM12878") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

#K562
all_varimps_K562_chromstates <- cbind.data.frame(varimp_K562_5kb$Feature,
                                        varimp_K562_5kb$aveimp5kb,         
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562_chromstates) <- c("Feature", "ave5kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562_chromstates <- all_varimps_K562_chromstates[order(rowMeans(all_varimps_K562_chromstates[,-1]), decreasing = TRUE),]
#all_varimps_K562_chromstates <- all_varimps_K562_chromstates[1:20,]
all_varimps_K562_chromstates <- melt(all_varimps_K562_chromstates)

b <- ggplot(all_varimps_K562_chromstates, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  ggtitle("K562") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "lightblue",
                      midpoint = 50,
                      high = muted("blue"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

@@

###5kb

```{r}
varimp_gm12878_5kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_gm12878_5kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)		
	  varimps <- varimps[order(varimps$Feature),]

		varimp_gm12878_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_gm12878_5kb <- data.frame(Feature = rownames(varimp_gm12878_5kb),
                                  aveimp5kb = rowMeans(varimp_gm12878_5kb, na.rm = TRUE),
                                  sdimp5kb = apply(varimp_gm12878_5kb,1, sd, na.rm = TRUE))
rownames(varimp_gm12878_5kb) <- NULL

@@

###5kb

```{r}
varimp_K562_5kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_K562_5kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

		varimp_K562_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_K562_5kb <- data.frame(Feature = rownames(varimp_K562_5kb),
                                  aveimp5kb = rowMeans(varimp_K562_5kb, na.rm = TRUE),
                                  sdimp5kb = apply(varimp_K562_5kb,1, sd, na.rm = TRUE))
rownames(varimp_K562_5kb) <- NULL

@@

```{r}
#GM12878
all_varimps_gm12878_histones <- cbind.data.frame(varimp_gm12878_5kb$Feature,
                                        varimp_gm12878_5kb$aveimp5kb,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878_histones) <- c("Feature", "ave5kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878_histones <- all_varimps_gm12878_histones[order(rowMeans(all_varimps_gm12878_histones[,-1]), decreasing = TRUE),]
#all_varimps_gm12878_histones <- all_varimps_gm12878_histones[1:20,]
all_varimps_gm12878_histones <- melt(all_varimps_gm12878_histones)

a2 <- ggplot(all_varimps_gm12878_histones, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("Histone Modification") +
  ggtitle("GM12878") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))

#K562
all_varimps_K562_histones <- cbind.data.frame(varimp_K562_5kb$Feature,
                                        varimp_K562_5kb$aveimp5kb,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562_histones) <- c("Feature", "ave5kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562_histones <- all_varimps_K562_histones[order(rowMeans(all_varimps_K562_histones[,-1]), decreasing = TRUE),]
#all_varimps_K562_histones <- all_varimps_K562_histones[1:20,]
all_varimps_K562_histones <- melt(all_varimps_K562_histones)

b2 <- ggplot(all_varimps_K562_histones, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("") +
  ylab("") +
  ggtitle("K562") +
  scale_fill_gradient2(limits=c(0,100),
                      low = "white",
                      mid = "lightblue",
                      midpoint = 50,
                      high = muted("blue"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size = 20))
